---
title: "Asset Types"
author: "Kristin Yeager"
date: "August 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Before You Use

The LibGuides V1.1 API requires a LibGuides CMS subscription, so if your institution does not have a CMS subscription, you will not be able to use this package.

Your site ID and API key can be found in your LibGuides system under Tools > API. Go to the Endpoints V1.1 tab, then click the GET Guides link.


## Basic Use

### Guides

Retrieve all guides in your system (replace `your_siteid` and `your_key` with your institution's site ID and API key):

```
myguides <- get_guides_data(siteID=your_siteid, 
                            key=your_key,
                            expand_pages=FALSE)
```

Retrieve all guide _pages_ in your system:

```
myguidepages <- get_guides_data(siteID=your_siteid, 
                                key=your_key,
                                expand_pages=TRUE)
```



### Assets

The `GET assets` API by default retrieves all asset types; however, this results in a massive download. If you are interested in downloading book assets, database assets, or file assets, then the functions `get_book_assets()`, `get_database_assets()`, and `get_file_assets()` are convenience functions for retrieving those asset types, respectively. 

```
mybooks <- get_book_assets(siteID=your_siteid, 
                            key=your_key)
```

If desired, the `options` argument can be used to specify other querystring parameters as described on the API page in your LibGuides system. For example, if I wanted to retrieve all document/file assets that appear on the SAS Tutorials (guide ID: 278271) and SPSS Tutorials (guide ID: 278275) LibGuides, I could run:

```
myfiles <- get_file_assets(siteID=your_siteid, 
                           key=your_key,
                           options="&guide_ids[]=278271&guide_ids[]=278275")
```

Note that the string you supply to the `options` argument will almost always start with an ampersand (&).


### Advanced Usage

To retrieve other asset types, you will want to use the `call_LG_api()` function. The `GET assets` API querystring parameter `asset_types` can be used to filter the asset types to one or more specific types, using the following codes:

```
1 - Rich Text/HTML
2 - Link
3 - RSS Feed
4 - Document / File
5 - Book from the Catalog
6 - Poll
7 - Google Search
9 - Media / Widget
10 - Database
11 - Guide List
12 - LibAnswers Widget
13 - LibWizard Item
```

For example, to get a list of link assets:

```{r}
#' Make API call - returns JSON output
mylinks <- call_LG_api(siteID=your_siteid,
                       key=your_key,
                       content="assets",
                       options="&asset_types=2")

#' Convert JSON output to dataframe
mylinks <- jsonlite::fromJSON(mylinks)
mylinks <- jsonlite::flatten(mylinks)
```






